\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
lol
almost

This paper presents a systematic mapping study on design pattern detection
methods.
It is organized as follows: 
 The first section explains the systematic mapping process
 The second section explains the selection process results
 The third one deals analyses the study results
 The article then continues with the limitations of our study
 It finishes with related work.

@@

Another strong

@@

For behavioural pattern, static analysis migh be sufficient but a majority of
article includes a dynamic component to the anaylis.
Tsantalis et al.[325] had good result with their graph similarity scoring
approach for detecting structural and behavioural pattern with a static method.

>>>>

This paper presents a systematic mapping study on design pattern detection
methods.
It is organized as follows: 
 the first section explains the systematic mapping process,
 the second section explains the selection process results,
 the third one deals analyses the study results,
 the article then continues with the limitations of our study,
 and it concludes with related works.

@@

Another big avenue for detection strategy lies in artificial intelligence
and machine learning.
In fact, a fifth of the articles make use an AI technique.

Graph methods are popular popular and half the time have been used jointly with
pattern matching techniques.

@@

For behavioural pattern, static analysis migh be sufficient but a majority of
article includes a dynamic component to the anaylis.
Tsantalis et al.\cite{6} had good result with their graph similarity scoring
approach for detecting structural and behavioural pattern with a static method.

Kaczor et al.\cite{4} use an hybrid graph matching algorithm to detect creationnal
and structural design pattern.
